\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.5cm]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{microtype}
\DisableLigatures{encoding = *, family = * }

\newcommand{\hrefmailto}[2]{\href{#1 mailto:#2}{#2}}

\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{Gonzalo Oviedo Lambert}} \\
    \vspace{2pt}
    Limache, Valparaíso Region, Chile \\
    \vspace{2pt}
    \hrefmailto{goviedo.sevenit@gmail.com}{goviedo.sevenit@gmail.com} | +56 9 6372 3603 \\
    \href{https://www.linkedin.com/in/gol}{linkedin.com/in/gol}
\end{center}

\section*{Professional Summary}
\hrule
\vspace{5pt}
\noindent
I am a \textbf{Senior Software Engineer} with over 15 years of experience developing critical and scalable applications. My core expertise lies in the \textbf{Java (Spring Boot)} ecosystem, complemented by strong specialization in \textbf{SQL (Oracle and PostgreSQL)}.

I have contributed to high-demand sectors such as \textbf{Finance (Citibank), EdTech (WebClass), and E-commerce (Perficient/Caterpillar)}. My profile is \textit{full-cycle}: infrastructure as code (\textbf{IaC}) using \textbf{Pulumi on Google Cloud Platform}, and I have led the development of modern interfaces with \textbf{React and Flutter}. My current focus combines building robust platforms, efficient microservices migration, exploration of emerging technologies like \textbf{Blockchain (Cardano, ICP, Solidity)}, and adoption of high-performance technologies like \textbf{Elixir and Ash Framework} to solve basic and complex business problems with elegant technical solutions.

\section*{Technical Skills}
\hrule
\vspace{5pt}
\textbf{Languages:} Java (1.8+), Elixir, Javascript (ES6+), SQL, Bash. \\
\textbf{Frameworks:} Spring Boot, Ash Framework, Vue.js, Nuxt, React, Struts. \\
\textbf{Infrastructure/Cloud:} Docker, Google Cloud (VM), Azure DevOps, AWS Lambda. \\
\textbf{Databases:} PostgreSQL, Oracle PL/SQL, MongoDB, MySQL.

\section*{Recent Experience}
\hrule
\vspace{5pt}
\textbf{CTO \& Co-founder} | \textit{Mobility Startup} \hfill 2024 -- Present \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Technical leadership in developing a mobility platform using Elixir and Ash Framework.
    \item Building the entire tech stack, including Flutter applications and Java 21 (Spring Boot) services with GraalVM builds.
    \item Using Google Cloud with Pulumi to generate automated cloud infrastructure transition.
\end{itemize}

\vspace{8pt}

\textbf{Java Associative Developer} | \textit{Perficient - Caterpillar} \hfill 2022 -- 2023 \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Development and maintenance of the global e-commerce system using Java and agile methodologies.
    \item Collaboration in multicultural teams from USA, India, and Latin America.
\end{itemize}

\vspace{8pt}

\textbf{Java Specialist} | \textit{Citibank} \hfill 2021 -- 2022 \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Development of solutions for monthly requirements using internal framework (Java Bean Spring).
    \item Creation and maintenance of reports for internal clients.
    \item Database migration from Sybase to Oracle in multicultural team (USA, Ukraine, India, Chile).
    \item Tools: Java, Oracle SQL, Spring Beans, Jenkins, Jira, Confluence, Git, Eclipse, Gradle, Websphere.
\end{itemize}

\vspace{8pt}

\textbf{CTO} | \textit{Seven IT SpA (Hospital Cruz del Norte, SQM)} \hfill 2017 -- 2020 \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Owner, manager, and developer of Health Management System for hospital care control and records (medicine, nursing, kinesiology).
    \item Development of payment management module and specific reports for administration in PDF.
    \item Functional and technical leadership managing a team of 4 developers (front and backend).
    \item Tools: Spring Boot (REST, MVC), PostgreSQL 9.6, Linux, Google Cloud (VM), Gitlab, jQuery, JavaScript, Bootstrap, Vuetify.
\end{itemize}

\section*{Education}
\hrule
\vspace{5pt}
\textbf{Bachelor's Degree in Computer Science and Informatics} | Universidad del Bío Bío \\
Thesis: Extreme Programming (XP) - Theory and practice.

\end{document}