\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.5cm]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{microtype}
\DisableLigatures{encoding = *, family = * }

\usepackage{helvet}
\pagestyle{empty}

\begin{document}

% ENCABEZADO
\begin{center}
    {\LARGE \textbf{Gonzalo Oviedo Lambert}} \\
    \vspace{2pt}
    \textit{FullStack Java Developer - Flutter - Javascript - SQL - GCP} \\
    \vspace{2pt}
    Limache, Valparaíso Region, Chile | GMT-4 - UTC-4 \\
    \vspace{2pt}
    \href{gonzalo.oviedo.dev@gmail.com}{gonzalo.oviedo.dev@gmail.com} | +56 9 6372 3603 \\
    \href{https://www.linkedin.com/in/gol}{linkedin.com/in/gol} | English Intermediate B1
\end{center}

\section*{Professional Summary}
\hrule
\vspace{5pt}
\noindent
I am a \textbf{Senior Software Engineer} with over 15 years of experience in developing critical and scalable applications. My core expertise lies in the \textbf{Java (Spring Boot)} ecosystem, complemented by a solid specialization in \textbf{SQL (Oracle and PostgreSQL)}.

\par\vspace{8pt}

\noindent
I have contributed in high-demand sectors such as \textbf{Finance (Citibank), EdTech (WebClass) and E-commerce (Perficient/Caterpillar)}. My profile is full-cycle (\textit{Full-cycle}): infrastructure as code (\textbf{IaC}) using \textbf{Pulumi on Google Cloud Platform}, and I have led the development of modern interfaces mostly with \textbf{Flutter}. I am passionate about creating robust platforms, exploring emerging technologies such as \textbf{Blockchain (ICP, Solidity)} and adopting high-performance technologies such as \textbf{Elixir and Ash Framework}. I enjoy working in collaborative teams seeking solutions that add real business value.

\section*{Technical Skills}
\hrule
\vspace{5pt}
\textbf{Primary Skills} \\[6pt]
\textbf{Languages:} Java (1.8 - 21), SQL \\
\textbf{Frameworks:} Spring Boot \\
\textbf{Databases:} PostgreSQL, Oracle PL/SQL \\
\textbf{Cloud/Infrastructure:} Google Cloud (Pulumi IaC), Docker \\
\textbf{AI:} Agentic AI with Pi.dev \\[6pt]
\textbf{Secondary Skills} \\[6pt]
\textbf{Languages:} JavaScript (ES6+), Bash, Elixir \\
\textbf{Frameworks:} Vue.js, Nuxt, React, Struts, Ash Framework \\
\textbf{Infrastructure/Cloud:} Azure DevOps, AWS Lambda \\
\textbf{Databases:} MongoDB, MySQL \\
\textbf{Blockchain:} Solidity, Internet Computer

\section*{Recent Experience}
\hrule
\vspace{8pt}
\textbf{CTO \& Co-founder} | \textit{Mobility Startup} \hfill 2024 -- Present \\
\textbf{Technologies:} Elixir, Ash Framework, Flutter, Java 21 (Spring Boot), GraalVM, Google Cloud, Pulumi, Agentic AI with Pi.dev \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Architecture and development of mobility platform powered by Agentic AI with Pi.dev, designing and implementing the agent lifecycle (skills, commands, workflow) as execution harness and integrating cost-effective LLMs without sacrificing performance.
    \item Construction of the complete tech stack and leadership of the technical team.
    \item Implementation of automated cloud infrastructure with Pulumi.
\end{itemize}
\vspace{8pt}
\textbf{Java Associative Developer} | \textit{Perficient - Caterpillar} \hfill 2022 -- 2023 \\
\textbf{Technologies:} Java 21 (Spring Boot) \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Development and maintenance of the global e-commerce system using Java and agile methodologies.
    \item Collaboration in multicultural teams from USA, India and Latin America.
\end{itemize}
\vspace{8pt}
\textbf{Java Specialist} | \textit{Citibank} \hfill 2021 -- 2022 \\
\textbf{Technologies:} Java, Oracle SQL, Spring Beans, Jenkins, Jira, Confluence, Git, Eclipse, Gradle, Websphere \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Development of solutions for monthly requirements using internal framework (Java Bean Spring).
    \item Creation and maintenance of reports for internal clients.
    \item Migration of Sybase database to Oracle in multicultural team (USA, Ukraine, India, Chile).
\end{itemize}
\vspace{8pt}
\textbf{CTO} | \textit{Seven IT SpA (Hospital Cruz del Norte, SQM)} \hfill 2017 -- 2020 \\
\textbf{Technologies:} Spring Boot (REST, MVC), PostgreSQL 9.6, Linux, Google Cloud (VM), Gitlab, jQuery, JavaScript, Bootstrap, Vuetify \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Owner, manager and developer of Health Management System for hospital care control and records (medicine, nursing, kinesiology).
    \item Development of payment management module and specific reports for administration in PDF.
    \item Functional and technical leadership managing a team of 4 developers (front and backend).
\end{itemize}
\vspace{8pt}
\textbf{Java/Senior Developer} | \textit{WebClass, Creasys, Coopeuch, Others} \hfill 2008 -- 2017 \\
\textbf{Technologies:} Java, AS/400, Struts, Hibernate, PostgreSQL, Oracle, SQL Server, Jenkins, Jira \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Full-cycle development: requirements analysis, design, development, QA for banking, ed-tech and enterprise.
    \item Team leadership and collaboration in multicultural environments (Santander, Ripley, Coopeuch).
    \item Electronic invoicing, banking migrations (AS/400 to Java), incident management.
    \item Generation of additional sales through new features in educational platforms (1,800 schools).
\end{itemize}

\section*{Education}
\hrule
\vspace{5pt}
\textbf{Computer Science Engineering Technician} | Universidad del Bío Bío \\
Thesis: Extreme Programming (XP) - Theory and Practice.

\end{document}
