\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.5cm]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{microtype}
\DisableLigatures{encoding = *, family = * }

\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{Gonzalo Oviedo Lambert}} \\
    \vspace{2pt}
    CTO | Full Stack Software Engineer | Software Architect \\
    \vspace{2pt}
    Limache, Valparaiso Region, Chile \\
    \vspace{2pt}
    \href{mailto:goviedo.sevenit@gmail.com}{goviedo.sevenit@gmail.com} | +56 9 6372 3603 \\
    \href{https://www.linkedin.com/in/gol}{linkedin.com/in/gol} | \href{https://sevenit.cl/}{sevenit.cl}
\end{center}

\section*{Professional Summary}
\hrule
\vspace{5pt}
\noindent
Full Stack Software Engineer and Architect with over 15 years of experience building critical and scalable systems. As CTO and Co-Founder of Te Llevo (Mobility Startup), I designed and built from scratch a complete high-performance mobility platform using Java 21 (Spring Boot) compiled with GraalVM, Flutter/Dart for mobile applications, and Infrastructure as Code (IaC) on Google Cloud Platform with Pulumi.

Previously, as CTO of Seven IT SpA (2017-2020), I served as the principal architect of the Health Management System for Hospital Cruz del Norte and SQM, leading a team of 4 developers with Spring Boot and PostgreSQL on Google Cloud.

I have driven digital transformation across high-demand sectors including finance (Citibank), global e-commerce (Caterpillar/Perficient), healthcare, education, and mobility. My approach combines senior-level technical depth with strategic leadership and a strong business-oriented mindset.

Key technologies: Java (Spring Boot), Flutter, React, Pulumi, GCP, Docker, microservices, PostgreSQL, Oracle, Elixir, Ash Framework, Blockchain (ICP/Solidity).

\section*{Technical Skills}
\hrule
\vspace{5pt}
\textbf{Languages:} Java (1.8+, 21), Elixir, JavaScript (ES6+), SQL, PL/SQL, Bash, Solidity. \\
\textbf{Frameworks:} Spring Boot, Ash Framework, Flutter, React, Vue.js, Nuxt, Struts, Hibernate, ExtJS. \\
\textbf{Infrastructure and Cloud:} Docker, Google Cloud Platform (VM, Cloud Run), Pulumi (IaC), AWS Lambda, Azure DevOps, Jenkins, Git, Gitlab, GraalVM. \\
\textbf{Databases:} PostgreSQL, Oracle (PL/SQL), MongoDB, MySQL, SQL Server, Sybase. \\
\textbf{Blockchain:} Solidity, Internet Computer (ICP). \\
\textbf{Methodologies:} Scrum, CI/CD, DevOps, Microservices.

\section*{Professional Experience}
\hrule
\vspace{5pt}

\textbf{CTO and Co-Founder} | \textit{Te Llevo App} \hfill November 2023 -- Present \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Led end-to-end technical architecture and delivery of a scalable mobility platform from the ground up.
    \item Built mobile applications in Flutter/Dart and backend services in Java 21 (Spring Boot) compiled with GraalVM for native-level performance.
    \item Designed high-throughput services using Elixir and Ash Framework, achieving lower resource consumption and faster response times.
    \item Implemented Infrastructure as Code (IaC) with Pulumi on Google Cloud Platform, fully automating provisioning and deployment pipelines.
    \item Established microservices architecture, robust CI/CD pipelines, and a quality-driven team culture across a multidisciplinary squad.
    \item Key impact: Delivered a modern, scalable full-stack mobility solution while optimizing performance and reducing operational costs.
\end{itemize}

\vspace{8pt}

\textbf{Analyst and Developer} | \textit{Salcobrand} \hfill December 2023 -- December 2025 \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Developed and analyzed software solutions for the retail and healthcare sectors.
    \item Implemented integrations and enhancements across mission-critical business systems.
\end{itemize}

\vspace{8pt}

\textbf{Software Developer} | \textit{Perficient (Caterpillar)} \hfill November 2022 -- June 2024 \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Developed and maintained the global e-commerce platform using Java and agile methodologies.
    \item Collaborated within multicultural teams spanning the United States, India, and Latin America.
\end{itemize}

\vspace{8pt}

\textbf{Senior Developer / Tax Developer Specialist} | \textit{Kibernum Chile (Citibank)} \hfill April 2021 -- November 2022 \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Built solutions for monthly tax requirements using the internal Java Bean Spring framework.
    \item Executed database migration from Sybase to Oracle within a cross-functional, international team (USA, Ukraine, India, Chile).
    \item Tools: Java, Oracle SQL, Spring Beans, Jenkins, Jira, Confluence, Git, Eclipse, Gradle, Websphere.
\end{itemize}

\vspace{8pt}

\textbf{Full Stack Developer} | \textit{WebClass (Creasys)} \hfill April 2020 -- May 2021 \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Delivered full-stack development for an educational platform reaching over 1,800 schools.
    \item Drove revenue growth through new feature development on the platform.
\end{itemize}

\vspace{8pt}

\textbf{CTO and IT Project Director} | \textit{Seven IT SpA (Hospital Cruz del Norte, SQM)} \hfill February 2017 -- May 2021 \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Served as principal architect and developer of a Health Management System covering medical, nursing, and kinesiology care records.
    \item Built a comprehensive payment management module with PDF report generation for hospital administration.
    \item Led a 4-developer team (frontend and backend) with both functional and technical accountability.
    \item Developed a retail product solution using Sencha ExtJS 4.1 (MVC), PHP backend, and SQL Server.
    \item Tools: Spring Boot (REST, MVC), PostgreSQL 9.6, Linux, Google Cloud (VM), Gitlab, jQuery, JavaScript, Bootstrap, Vuetify.
\end{itemize}

\vspace{8pt}

\textbf{Full Stack Developer} | \textit{Nubox Chile} \hfill January 2015 -- January 2017 \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Developed full-stack software solutions for accounting and tax management platforms.
\end{itemize}

\vspace{8pt}

\textbf{Incident Management} | \textit{ISBAN - Santander Group} \hfill October 2013 -- January 2015 \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Managed incidents for the Banking and Mutual Fund divisions at Santander.
\end{itemize}

\vspace{8pt}

\textbf{Project Lead / Software Engineer / QA Analyst} | \textit{Coopeuch} \hfill April 2010 -- October 2013 \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Led projects, developed software, and performed QA analysis for the financial cooperative.
    \item Managed full-cycle delivery: requirements analysis, design, development, testing, and deployment.
\end{itemize}

\vspace{8pt}

\textbf{Software Analyst} | \textit{ADNet Consulting} \hfill April 2008 -- April 2010 \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Developed solutions in PL/SQL and Java/JEE.
    \item Built an office asset management system with approval workflows using Hibernate and Struts.
\end{itemize}

\vspace{8pt}

\textbf{Java / J2EE Developer} | \textit{ADA - Soluciones Informaticas} \hfill August 2005 -- March 2008 \\
\begin{itemize}[noitemsep, topsep=0pt]
    \item Developed Java/J2EE applications for BCI banking systems.
\end{itemize}

\section*{Education}
\hrule
\vspace{5pt}
\textbf{Computer Science and Informatics Engineering Degree} | Universidad del Bio Bio \hfill 1998 -- 2005

\section*{Certifications}
\hrule
\vspace{5pt}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Absolute Introduction to Object Oriented Programming in Java
    \item Build an LLM-powered Chatbot with RAG using LlamaIndex
    \item SOLID Principles: Introducing Software Architecture and Design
    \item DevOps, CI/CD (Continuous Integration/Deliver) for Beginners
\end{itemize}

\section*{Languages}
\hrule
\vspace{5pt}
Spanish (Native) | English (Full Professional)

\end{document}